Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-05-31 ms.tex
some fix-up of reddening discussion

To achieve this empirical calibration, we must adopt a set of calibrator
objects for which true optical reddening is known. There are various 
possibilities at our disposal. \cite{planckdust} calibrated their $\tau_{353}$ 
to $E(B-V)$ using broadband Sloan Digital Sky Survey \citep[SDSS;][]{sdss} 
photometry for a set of $\sim$10$^5$ quasars. The SFD calibration was 
originally tied to a sample of 384 elliptical galaxies, but was later revised 
by \cite{schlafly11} using $\sim$250,000 stars with both spectroscopy and 
broadband photometry available from SDSS. To calibrate our $\tau_{545}$ to 
reddening, we make use of the same set of stars studied by \cite{schlafly11}.

@@

Given a library of stellar atmosphere models, the spectral lines of these stars
can be used to predict their intrinsic optical broadband colors. The `true' 
reddening is then simply the difference in the observed $g-r$ color and the 
$g-r$ color predicted from the spectral lines. Applying a color transformation 
then yields `true' $E(B-V)$ values for $\sim$250,000 lines of sight, mostly at 
high Galactic latitude. The calibration of two-component optical depth to 
$E(B-V)$ is then performed as a linear regression of $E(B-V)_{SSPP}$ versus 
$\tau_{545}$. $\tau_{545}$ is considered to be the independent variable in this
regression, as we ultimately wish to predict $E(B-V)$ as a function of optical 
depth, and $\tau_{545}$ has much higher S/N than the SSPP $E(B-V)$ estimates.

@@

The result of this regression is shown in Figure \ref{fig:calib}. Indeed there 
appears to be a strong linear correlation between $E(B-V)_{SSPP}$ 
and $\tau_{545}$. The conversion factor from $\tau_{545}$ to $E(B-V)$ is 
2.41$\times$10$^{3}$. Reassuringly, the best-fit offset is quite close to 
zero, $\sim$3 mmag.

@@

\begin{figure}
\begin{center}
\epsfig{file=ebv_resid.eps, width=2.5in, angle=90}
\caption{\label{fig:resid} $E(B-V)_{2comp}$ residuals as a function of
SFD $E(B-V)$. The grayscale represents the conditional probability within each
bin in SFD $E(B-V)$. The central black line shows the moving median. The upper
and lower black lines represent the moving 75th and 25th percentiles 
respectively.}
\end{center}
\end{figure}

>>>>

To achieve this empirical calibration, we must adopt a set of calibrator
objects for which true optical reddening is known. There are various 
possibilities at our disposal. \cite{planckdust} calibrated their radiance 
and $\tau_{353}$ maps to $E(B-V)$ using broadband Sloan Digital Sky Survey 
\citep[SDSS;][]{sdss} photometry for a set of $\sim$10$^5$ quasars. The SFD 
calibration was originally tied to a sample of 384 elliptical galaxies, but was
later revised by \cite{schlafly11} using $\sim$250,000 stars with both 
spectroscopy and broadband photometry available from SDSS. To calibrate our 
$\tau_{545}$ to reddening, we make use of the same set of stars studied by 
\cite{schlafly11}.

@@

Given a library of stellar atmosphere models, the spectral lines of these stars
can be used to predict their intrinsic optical broadband colors. The `true' 
reddening is then simply the difference in the observed $g-r$ color and the 
$g-r$ color predicted from the spectral lines. Applying a color transformation 
then yields `true' $E(B-V)$ values for $\sim$260,000 lines of sight. Throughout
our SSPP calibration analysis, we restrict to the $\sim$230,000 lines of sight 
with $|b|$$>$20$^{\circ}$ in order to avoid stars which may not lie behind the 
full dust column. The calibration of two-component optical depth to $E(B-V)$ is
performed as a linear regression of $E(B-V)_{SSPP}$ versus $\tau_{545}$. 
$\tau_{545}$ is considered to be the independent variable in this regression, 
as we ultimately wish to predict $E(B-V)$ as a function of optical depth, and 
$\tau_{545}$ has much higher S/N than the SSPP $E(B-V)$ estimates.

@@

The result of this regression is shown in Figure \ref{fig:calib}. Indeed there 
appears to be a strong linear correlation between $E(B-V)_{SSPP}$ 
and $\tau_{545}$. The conversion factor from $\tau_{545}$ to $E(B-V)$ is 
2.46$\times$10$^{3}$. Reassuringly, the best-fit offset is quite close to 
zero, $\sim$0.6 mmag.

@@

\begin{figure}
\begin{center}
\epsfig{file=ebv_resid.eps, width=3.3in}
\caption{\label{fig:resid} $E(B-V)_{2comp}$ residuals as a function of
SFD $E(B-V)$. The grayscale represents the conditional probability within each
bin in SFD $E(B-V)$. The central black line shows the moving median. The upper
and lower black lines represent the moving 75th and 25th percentiles 
respectively.}
\end{center}
\end{figure}
